Bayesian phylogenetic estimation of fossil ages reveals remarkable consistency of rocks and clocks

### 2015-08-25 fossilDating.tex
canids
incorporated Tanja's changes

% Papers
% http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4033271/ Beyond fossil calibrations: realities of molecular clock practices in evolutionary biology
% http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0066245 A Simple Method for Estimating Informative Node Age Priors for the Fossil Calibration of Molecular Divergence Time Analyses
% http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3108556/  Bayesian Phylogenetic Method to Estimate Unknown Sequence Ages

@@

\subsection*{Bayes factors}

The Bayes factor ($BF$) computes the evidence for one hypothesis ($H_1$) over another ($H_2$) as the ratio of the marginal probability of the data under each of the two hypotheses:

\begin{equation}
BF = \frac{\Pr\{D|H_1\}}{\Pr\{D|H_2\}} = \frac{p(H_1|D)}{p(H_2|D)}\frac{p(H_2)}{p(H_1)}
\end{equation}

We are interested in computing the Bayes factor that quantifies the amount of phylogenetic evidence in support of the geological age range for each fossil. In this case $H_1$ is the hypothesis that the true fossil age is within the given paleontological age range, and $H_2$ is the alternative hypothesis that the true fossil age is outside the geological range, but within the broader interval of $(0,160)$ Mya. So for each fossil the prior probability of $H_1$, $p(H_1)$, is easily computed as the width of the geological range divided by 160 and the prior probability of the alternative is simply $p(H_2) = 1 - p(H_1)$. We assume a prior probability of zero that the fossil age is older than 160Mya. Likewise $p(H_1 | D)$ is the posterior probability that the age falls in the geological range and $p(H_2 | D) = 1 - p(H_1 | D)$. Thus computing the Bayes factor in this instance is easy to do for each fossil once a posterior distribution of the phylogenetic age of the fossil is obtained under a Uniform prior from $(0,160)$ Mya.

\subsection*{Bayes factor - update Tanja}

>>>>

% Papers
% http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4033271/ Beyond fossil calibrations: realities of molecular clock practices in evolutionary biology
% http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0066245 A Simple Method for Estimating Informative Node Age Priors for the Fossil Calibration of Molecular Divergence Time Analyses
% http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3108556/  Bayesian Phylogenetic Method to Estimate Unknown Sequence Ages
% http://www.pnas.org/content/112/16/4897 Canids

@@

\subsection*{Bayes factor}
